test-mcda

### 2024-05-24 code/MCDA-EVSE.Rmd
full analysis

#quantiles <- classIntervals(TOPSIS_toplot$values, n = 8, style = "quantile")
#TOPSIS_toplot$quantile <- cut(TOPSIS_toplot$values, breaks = quantiles$brks, include.lowest = TRUE)

ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=TOPSIS_toplot, color="black", aes(fill=values)) #+ scale_fill_brewer(palette = "Blues")
```

@@

>>>>

quantiles <- classIntervals(TOPSIS_toplot$values, n = 8, style = "quantile")
TOPSIS_toplot$quantile <- cut(TOPSIS_toplot$values, breaks = quantiles$brks, include.lowest = TRUE)

ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=TOPSIS_toplot, color="black", aes(fill=quantile))+ scale_fill_brewer(palette = "RdBu")
```

@@

  mutate(score = 
  0.12*scl_density + 
  0.18*scl_evse_re +
  0.15*scl_elec + 
  0.1*scl_drivingpop +
  0.1*scl_parking_re + 
  0.05*scl_policefire_re + 
  0.05*zone_score + 
  0.12*scl_acc_re +
  0.13*scl_elect_use)

crit <- c("density","evse","ev", "drivingpop", "parking", "policefire", "zoning", "acc", "electricity")

criteriaWeightsPairwiseComparisons <- matrix(c(1.0, 3.0, 2.0, 1/2, 1/2, 1/4, 1/3, 1.5, 1.2,
                                               1/3, 1.0, 1/1.2, 1/4, 1/4, 1/8, 1/6, 1/2, 1/1.5, 
                                               1/2, 1.2, 1.0, 1/3, 1/3, 1/6, 1/6, 1/2, 1/1.5, 
                                               2, 4, 3, 1.0, 1/1.2, 1/4, 1/5, 1.5, 1.8,
                                               2, 4, 3, 1.2, 1.0, 1/4, 1/4, 2, 1.5, 
                                               4, 8, 6, 4, 4, 1, 1.2, 3, 2,
                                               3, 6, 6, 5, 4, 1/1.2, 1, 3, 2,
                                               1/1,5, 2, 2, 1/1.5, 1/2, 1/3, 1/3, 1, 1.5, 
                                               1/1.2, 1.5, 1.5, 1/1.8, 1/1.5, 1/2, 1/2, 1/1.5, 1
                                               ),
nrow=length(crit),
ncol=length(crit),
dimnames=list(crit,crit))

column_sums <- colSums(criteriaWeightsPairwiseComparisons)

# Divide each element by the sum of its column
normalized_matrix <- sweep(criteriaWeightsPairwiseComparisons, 2, column_sums, FUN = "/")

# Step 3: Calculate the weights
# Calculate the average of each row
weights <- rowMeans(normalized_matrix)

# Output the weights
print(weights)

# reverse is min
weights <- c(0.249, 0.114, 0.105, 0.098, 0.1909, 0.074, 0.033, 0.033, 0.102)
criteriaMinMax <- c("min", "max", "max", "min", "max", "min", "min", "max", "max")
# positiveIdealSolutions <- c(0.17, 0.60, 0.70, 0, 0.50, 0.10, 0.14, 0.3,0.007)
overall2 <- TOPSIS(performanceTable, weights, criteriaMinMax)
AHP_TOPSIS <- data.frame(uniqueID = names(overall2), values = overall2) %>%  
  mutate(uniqueID = as.integer(uniqueID))

AHP_TOPSIS_toplot <- fishnet_nowater %>% 
  left_join(TOPSIS, by = "uniqueID")

quantiles <- classIntervals(AHP_TOPSIS_toplot$values, n = 8, style = "quantile")
AHP_TOPSIS_toplot$quantile <- cut(AHP_TOPSIS_toplot$values, breaks = quantiles$brks, include.lowest = TRUE)

ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=AHP_TOPSIS_toplot, color="black", aes(fill=quantile)) + scale_fill_brewer(palette = "RdBu")
```

# Consistency Check

AHP_TOPSIS, TOPSIS, WSM, PROMETHEE

TOPSIS <- TOPSIS %>%
  mutate(topsis_rank = min_rank(desc(values)))

WSM <- WSM %>% 
  dplyr::select(c(uniqueID, score)) %>% 
  mutate(wsm_rank = min_rank(desc(score)))

PROMETHEE <- promethee_df %>% 
  mutate(promethee_rank = min_rank(desc(net)))

AHP_TOPSIS <- AHP_TOPSIS %>% 
  mutate(ahptopsis_rank = min_rank(desc(values)))

rank_compare <- WSM %>% 
  st_drop_geometry() %>% 
  dplyr::select(c(uniqueID, wsm_rank)) %>% 
  left_join(., TOPSIS %>% dplyr::select(uniqueID, topsis_rank), by = "uniqueID") %>% 
  left_join(., PROMETHEE %>% dplyr::select(uniqueID, promethee_rank), by = "uniqueID") %>% 
  left_join(., AHP_TOPSIS %>% dplyr::select(uniqueID, ahptopsis_rank), by = "uniqueID") %>% 
  mutate(avg_rank = (wsm_rank + topsis_rank + promethee_rank + ahptopsis_rank) / 4)

rank_toplot <- fishnet_nowater %>% 
  left_join(rank_compare, by = "uniqueID")
ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=rank_toplot, color="black", aes(fill=avg_rank))
```

### 2024-05-24 code/test-mcda.Rmd
full analysis

>>>>

# Step 1: Create the Pairwise Comparison Matrix
# Example matrix for three criteria
pairwise_matrix <- matrix(c(
  1,   3, 1/2,
  1/3, 1, 1/4,
  2,   4, 1
), nrow = 3, byrow = TRUE)

# Step 2: Normalize the Pairwise Comparison Matrix
# Calculate the sum of each column
column_sums <- colSums(pairwise_matrix)

# Divide each element by the sum of its column
normalized_matrix <- sweep(pairwise_matrix, 2, column_sums, FUN = "/")

# Step 3: Calculate the weights
# Calculate the average of each row
weights <- rowMeans(normalized_matrix)

# Output the weights
print(weights)
